---
title: "Homework 2"
author: "Jane Wei"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: html_document
---

#Abstract 
The study compared patients undergoing aortic surgery following one vs. multiple cardiac intervention. 

#Patients and methods
The data contains 360 subjects who had their first re-do aortic surgery and 69 subjects who had multiple re-do aortic surgeries. The four hundred and twenty-nine patients all came from the same US academic healthcare system. 
```{r, load-data}
# load Num_of_Redo data
setwd("./INFO_550")
library(dplyr)
library(survival)

Num_of_Redo <- read.csv(file='Num_of_Redo.csv', header=TRUE)
```

##Data Clean
First, the data has been imported to R and cleaned.
```{r, Data-Clean, echo = FALSE}
#Data clean code here
head(Num_of_Redo)
#Num_of_Redo< -Num_of_Redo%>%mutate(OR_length=(Skin_Incision_Stop_Date_And_Time-Skin_Incision_Start_Date_And_Time)/3600)

```

#Results
The Kaplan Meier survival curve for both group looks like this: 
```{r, KM, echo = FALSE}
#Survial code here
f1 <- survfit(Surv(Survival__years_, Alive_at_last_follow_up) ~ 1, data = Num_of_Redo)

plot(survfit(Surv(Survival__years_, Alive_at_last_follow_up) ~ 1, data = Num_of_Redo), 
     xlab = "Survival Years", 
     ylab = "survival probability")
```
#Discussion
As we see in Figure \@ref(fig:KM), the multiple redo group has a sharp drop within 30 days compare to the first redo group.

#Notes on the report 
Finally, A few reproducible related information were kept below. 
```{r, Appendix, echo = FALSE}
getwd()
devtools::session_info()
```

Rscript -e "rmarkdown::render('Homework2.Rmd')"
